### 2019-03-22 IEEE_TC_submission.d/intro.tex
ssr

\IEEEPARstart{T}{he} class of \textbf{canalyzing} Boolean functions, introduced 
in \cite{Kauffman-1969}, is defined as follows.

@@

@@

Over the years, a considerable amount of research on detecting symmetry properties 
of Boolean functions has been reported in the literature
(e.g., \cite{BS-1968,Biswas-1970,TM-1996,KS-2000,Darga-etal-2008,Maurer-2015}).
Several references have observed the usefulness of detecting symmetries
in automated logic synthesis (e.g., \cite{AP-2008,Hu-etal-2008,Darga-etal-2008}).
Reference \cite{Maurer-2015} provides a thorough discussion of known
symmetry detection algorithms and presents a new universal algorithm 
for detecting any form of permutation-based symmetry in Boolean functions. 
To our knowledge, relationships between NCFs and symmetric
Boolean functions have not been addressed in the literature.

>>>>

\IEEEPARstart{R}{search} on the symmetry properties of Boolean
functions has received a lot of attention from the
automated logic synthesis community. 
(Additional discussion on this is provided in Section~\ref{sse:related}.)
In this paper, we focus on the symmetry properties of
a class of Boolean functions (called \textbf{nested canalyzing functions})
which are used to model biological phenomena.
To define this class, we start with a simpler
class of functions, called \textbf{canalyzing} Boolean functions.
This class, introduced in \cite{Kauffman-1969}, is defined as follows.

@@

Over the years, a considerable amount of research on detecting symmetry properties 
of Boolean functions has been reported in the literature
(e.g., \cite{BS-1968,Biswas-1970,TM-1996,KS-2000,Darga-etal-2008,Maurer-2015}).
Several references have observed the usefulness of detecting symmetries
in automated logic synthesis (e.g., \cite{AP-2008,Hu-etal-2008,Darga-etal-2008}).
Reference \cite{Maurer-2015} provides a thorough discussion of known
symmetry detection algorithms and presents a new universal algorithm 
for detecting any form of permutation-based symmetry in Boolean functions.

@@

To our knowledge, relationships between NCFs and symmetric
Boolean functions have not been addressed in the literature.
